Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks

### 2015-10-21 manuscript/manuscript_wtc3.Rmd
pixiedust change

dust(resourcetab2)+
  sprinkle_colnames("Leaf", "Temperature", "LMA", "N~a~", "Vc~max~", "J~max~","K","WP~pre~","WP~mid~", paste0(greeks['delta'],"^13^c")) +
  sprinkle(rows= 1, part="head",bold=TRUE)+
  sprinkle_print_method("markdown")
```

@@

dust(getab2)+
  sprinkle_colnames("Leaf", "Light","Temperature", "A", "g~s~", "g~m~", "ITE","E","VPD","C~i~", "C~c~") +
  sprinkle(rows= 1, part="head",bold=TRUE)+
  sprinkle_print_method("markdown")
```

>>>>

dust(resourcetab2)%>%
  sprinkle_colnames("Leaf", "Temperature", "LMA", "N~a~", "Vc~max~", "J~max~","K","WP~pre~","WP~mid~", paste0(greeks['delta'],"^13^c")) %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

dust(getab2)%>%
  sprinkle_colnames("Leaf", "Light","Temperature", "A", "g~s~", "g~m~", "ITE","E","VPD","C~i~", "C~c~") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```
